---
title: "Homework 6"
date: "12/5/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  outout.width = "90%"
)
theme_set(theme_minimal()+theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour="viridis",
  ggplot2.continuous.fill="viridis"
)
scale_colour_discrete(scale_color_viridis_d())
scale_fill_discrete(scale_fill_viridis_d())
```

# Problem 2

```{r}
baby_df = read.csv("./birthweight.csv") %>% 
  mutate(
    babysex = as.factor(case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female"
    ))
  )
```


## My model

According to Love & Kinch (1965), the birth weight of baby is correlated with baby sex, the pre-pregnancy weight, height of mother, gestational age and maternal weight gain during pregnancy. 
Therefore, `babysex`, `ppwt`,`mheight`,`momage`and `wtgain` are included in the model.

Distribution of baby weight

```{r}
baby_df %>% ggplot(aes(x=bwt))+geom_density()
```

The baby birth weight is approximately normally distributed.

Build model

```{r}
mymodel = lm(bwt ~ babysex + ppwt + mheight + momage + wtgain, data=baby_df)
```

Prediction & residual

```{r}
baby_df %>% 
  modelr::add_residuals(mymodel) %>% 
  modelr::add_predictions(mymodel) %>% 
  ggplot(aes(x=pred, y=resid)) + geom_point() +geom_smooth()
```


## Model with length and sex

Look at the data

```{r}
baby_df %>% 
  ggplot(aes(x=blength,y=bwt))+
  geom_point()

baby_df %>% 
  ggplot(aes(x=gaweeks,y=bwt))+
  geom_point()
```

The plots suggests linear relationship

```{r}
sec_model = lm(bwt ~blength + gaweeks, data=baby_df)
```


## Model with interaction

```{r}
int_model = lm(bwt ~ bhead*blength*babysex,data=baby_df)
summary(int_model)
```

goodness of fit
```{r}
cv_df = crossv_mc(baby_df,100) %>% 
  mutate(
    train = map(train,as_tibble),
    test = map(test,as_tibble)
  )
```

```{r}
cb_df = cv_df %>% 
  mutate(
    my_model = map(train, ~lm(bwt ~ babysex + ppwt + mheight + momage + wtgain , data=.x)),
    main_effect_model = map(train, ~lm(bwt ~blength + gaweeks, data=.x)),
    int_model = map(train,~lm(bwt ~ bhead*blength*babysex,data=.x))
  ) %>% 
  mutate(
    rmse_my_model = map2(my_model,test,~rmse(model=.x, data=.y)),
    rmse_sec_model = map2(main_effect_model,test,~rmse(model=.x, data=.y)),
    rmse_int_model = map2 (int_model,test,~rmse(model=.x, data=.y))
  )
```

```{r}
cb_df %>% select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(model = fct_inorder(model),
         rmse = as.double(rmse)
         ) %>% 
  ggplot(aes(x=model, y=rmse)) + geom_violin()
```


Based on this comparison, we can conclude that the third model with head circumference, length, sex, and all interactions is more appropriate. 


# Problem 3

Import data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

















